Survival Compass: Statistical Insights into Lung Cancer Patients' Journey Post-Diagnosis

### 2024-04-04 paper/paper1.qmd
fixed and finished data section figures

@@

# Replace NA values with your desired stages
analysis_data <- analysis_data %>%
  mutate(pathogenic_stage = ifelse(is.na(pathogenic_stage), 
                                   c('Stage I', 'Stage IA', 'Stage IB', 
                                     'Stage II', 'Stage IIA', 'Stage IIB', 
                                     'Stage III', 'Stage IIIA', 'Stage IIIB', 
                                     'Stage IV'), 
                                   pathogenic_stage))

@@

# create bar chart for treatment decision
ggplot(treatment_decision_counts, aes(x = reorder(treatment_decision, -percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.2, color = "black", size = 3) +
  labs(title = "Percentage of Patients by Treatment Decision",
       x = "Treatment Decision",
       y = "Percentage") +
  theme_minimal() +
  coord_flip() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

# Create bar chart for treatment type
ggplot(treatment_type_counts, aes(x = reorder(treatment_type, -percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = "orange") +
  geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.2, color = "black", size = 3) +
  geom_text(data = treatment_type_counts, aes(label = treatment_type), hjust = 1.2, color = "black", size = 3) +
  labs(title = "Percentage of Patients by Treatment Type",
       x = "Treatment Type",
       y = "Percentage") +
  theme_minimal() +
  coord_flip() +
  scale_x_discrete(breaks = seq(0, max(treatment_type_counts$percentage), by = 5)) +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

>>>>

# read in data
analysis_data <- read.csv(file = here::here("data/analysis_data/lung_cancer_analysis_data.csv"))

@@

@@

# create bar chart for treatment decision
treatment_decision_counts <- analysis_data %>%
  group_by(treatment_decision) %>%
  summarise(count = n ()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  arrange(desc(treatment_decision))

ggplot(treatment_decision_counts, aes(x = reorder(treatment_decision, -percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = "blue") +
  geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.2, color = "black", size = 3) +
  labs(title = "Percentage of Patients by Treatment Decision",
       x = "Treatment Decision",
       y = "Percentage") +
  theme_minimal() +
  coord_flip() +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )

# Create bar chart for treatment type
treatment_type_counts <- analysis_data %>%
  group_by(treatment_type) %>%
  summarise(count = n ()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  arrange(desc(treatment_type))

ggplot(treatment_type_counts, aes(x = reorder(treatment_type, -percentage), y = percentage)) +
  geom_bar(stat = "identity", fill = "orange") +
  geom_text(aes(label = sprintf("%.1f%%", percentage)), hjust = -0.2, color = "black", size = 3) +
  geom_text(data = treatment_type_counts, aes(label = treatment_type), hjust = 1.2, color = "black", size = 3) +
  labs(title = "Percentage of Patients by Treatment Type",
       x = "Treatment Type",
       y = "Percentage") +
  theme_minimal() +
  coord_flip() +
  scale_x_discrete(breaks = seq(0, max(treatment_type_counts$percentage), by = 5)) +
  theme(
    text = element_text(family = "patrick") # Set font to Patrick Hand
  )
